Chapter 3: Insert title

### 2022-11-09 chapters/chp3.Rmd
add chapters folder and customize scripts

---
title: "Chapter 1: Insert title"
output: pdf_document
---

@@

@@

# Introduction {-}

Write intro.

@@

Section 1.

## Subsection

Write something interesting.

# New section

New section. See Figure \ref{fig:dumbbellrent} that reports the median share of ... The reference in the prior sentence cross-references and auto numbers your figures. This is prob one of the most useful things about writing your dissertation in R markdown. I add latex code to singlespace around the figure below. Be sure to add a ^[footnote.]

\begin{singlespace}
```{r dumbbellrent, results = "markup", fig.cap = "Median neighborhood rent burden rate for the highest 2019 rates, 2000 to 2019", out.width = "90%"}

knitr::include_graphics(here("figures/dumbbell_rent.jpeg"))

```
\end{singlespace}

@@

Write a good conclusion.

>>>>

---
title: "Chapter 3: Insert title"
output: pdf_document
---

@@

# functions

@@

# Introduction

This chapter

@@

Here is some code to insert a figure while also centering and single spacing. Note this has a .pdf suffix instead of .png. I usually use the latter because the file size is usually smaller and easier to work with in R.

\begin{center}
\begin{singlespace}
```{r flowchart, results = "markup", fig.cap = "Declining affordability mediates the effect of gentrification on displacement", out.width = "90%"}

knitr::include_graphics(here("figures/flow-chart.pdf"))

```
\end{singlespace}
\end{center}

## Sub-section

Write some more thoughts here.

@@

Conclude it.

You can add as many chapters as you want. My dissertation had 6 chapters. Just copy and modify an .Rmd file.
